### 2019-10-01 socials.tex
adds alt. socials

\begin{itemize}
	\item Cocktail Hour at Krannert Center for the Performing Arts\\
	Krannert is UIUC's world famous performance center with a beautiful lobby area capable of holding up to 2000 people. They have a cocktail bar on site as well as a stage in the lobby.
\end{itemize}

>>>>

\begin{itemize}
	\item \textbf{Cocktail Hour at Krannert Center for the Performing Arts}\\
	Krannert is UIUC's world famous performance center with a beautiful lobby area capable of holding up to 2000 people. They have a cocktail bar on site as well as a stage in the lobby.
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.5\textwidth]{krannert.jpg}
	\end{figure}
	\item \textbf{Illini Union Rec Room Lockout}\\
	The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at The Garden Hotel. This space can accompany up to 150 people, with extra overflow space with tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities. This will be an alcohol free social option.
	\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.75\linewidth]{union_recroom1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.75\linewidth]{union_recroom2.png}
	\end{subfigure}	
	\caption{Illini Union Rec Room}	
\end{figure}
	\item \textbf{The Illini Bar-nana Crawl}\\
	ANS-UIUC hosts an annual Bar-nana Crawl that combines social and public outreach aspects. This fun and hilarious (21+) social event includes a public outreach spin. Everyone will don a marvelous banana-suit costume and enjoy the great nightlife of downtown champaign. Discussing radiation dosage in terms of Banana Equivalent Dose (BED) is a popular way to demystify the risks of radiation. Banana suits would be included in the registration gift bag and potentially sponsored by an interested company. 
\end{itemize}
